Multi-Task Temporal and Spatial Networks for High-Precision Event Spotting in Volleyball Videos

### 2024-10-16 Paper.tex
Refactor Paper.tex for better organization and clarity

@@

\section{\uppercase{PROPOSED METHOD}}
\subsection{Problem Formulation}
\subsection{Model Architecture}
\subsubsection{Feature Extractor}
\subsubsection{Temporal Event Detection}
\subsubsection{Spatial Event Detection}
\subsubsection{Multi-Task Learning}
\subsubsection{Loss Function}

>>>>

% TODO:
%   [ ] Write Method
%   [ ] Write Experiments
%   [ ] Create Diagrams
    %   [ ] Model Architecture

@@

\section{\uppercase{PROPOSED METHOD}}
\subsection{Problem Formulation}
\textbf{Temporal Spatial Event Spotting (TSES)} aims to identify both the precise time and location of events within untrimmed videos. Given a video with \(N\) frames \(x_1, \ldots, x_N\) and a set of \(K\) event classes \(c_1, \ldots, c_K\), the goal is to predict a sparse set of frame indices where events occur, as well as the corresponding event class and spatial coordinates. Each prediction is represented as \((t, c_t, s_t)\), where \(t\) is the frame index, \(c_t\) is the predicted event class, and \(s_t\) is the spatial location of the event within that frame. A temporal prediction is considered correct if it falls within a small temporal tolerance \(\sigma_f\) frames of the labeled event and matches the ground-truth class. Similarly, spatial predictions are deemed correct if the distance between the predicted location \(s_t\) and the ground-truth event location is within a specified threshold \(\sigma_p\). For TSES, these tolerances are kept small, requiring precise frame-level accuracy, and it assumes that videos are captured with sufficiently high frame rates.

To perform well on this task, several key requirements must be met:
\begin{itemize}
    \item \textbf{Local Spatial-Temporal Features}: The model should capture subtle visual changes and movements across neighboring frames, essential for distinguishing between similar-looking moments.
    \item \textbf{Long-Term Temporal Context}: A broader temporal window allows the model to understand events in context, such as how player positions or actions evolve before and after a critical moment.
    \item \textbf{Dense Per-Frame Predictions}: For each frame \(x_t\), the model produces a prediction \((\hat{y}_t, \hat{s}_t)\), where \(\hat{y}_t \in \mathbb{R}^K\) is a one-hot vector representing the predicted event class probabilities, and \(\hat{s}_t \in \mathbb{R}^2\) represents the \(x, y\) coordinates of the event within the frame. This ensures frame-level precision for each event.
\end{itemize}

These requirements call for a robust and end-to-end trainable architecture capable of leveraging both temporal and spatial information. Our approach utilizes a sequence model that integrates local spatial-temporal features.

\subsection{Model Architecture}
\subsubsection{Feature Extractor}
\subsubsection{Temporal Event Detection}
\subsubsection{Spatial Event Detection}
\subsubsection{Multi-Task Learning}
\subsubsection{Loss Function}
